The Accuracy of KNN, SVM, Bayes classifier, SVDD, neural network with DBSCAN, k-means, NN-chain for Determining the Cancer by Gene-expression Signatures And the Arrhythmia Types

### 2023-05-31 final/paper/main.tex
update paper

  \begin{table*}[tb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques. (Arrhythmia dataset)}}
      \vspace{-\baselineskip}
    \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}lcccccccccccc@{}}\toprule
        Method                    & \multicolumn{2}{c}{Raw}                     & \multicolumn{2}{c}{Normalized}   & \multicolumn{2}{c}{PCA-32}        & \multicolumn{2}{c}{PCA-32 Normalized} & \multicolumn{2}{c}{AE-32}        & \multicolumn{2}{c}{AE-32 Normalized} \\ 
        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
                                  & Search (s) & acc                            & Search (s) & acc                 & Search (s) & acc                  & Search (s) & acc                      & Search (s) & acc                  & Search (s) & acc            \\ \midrule
      KNN-Brute-Force + DBSCAN    & $0.0285$   & $47.4684 \pm 0$                & $0.0254$   & $46.8354 \pm 0$     & $0.0070$   & $38.6076 \pm 0$      & $0.0071$   & $42.4051\pm 0$           & $0.0071$   & $\bf{37.9747} \pm 0$ & $0.0071$   & $\bf{44.3038} \pm 0$\\
      SVM (linear) + DBSCAN       & $1.7269$   & $25.9494 \pm 0$                & $8.9285$   & $35.4430 \pm 0$     & $0.2186$   & $32.2785 \pm 0$      & $0.8162$   & $29.7468 \pm 0$          & $0.2169$   & $31.6456 \pm 0$      & $0.1552$   & $27.8481 \pm 0$\\
      SVM (polynomial) + DBSCAN   & $0.9993$   & $25.9494 \pm 0$                & $1.6100$   & $25.3165 \pm 0$     & $0.1997$   & $\z{1.2658} \pm 0$   & $0.4577$   & $33.5443 \pm 0$          & $0.2402$   & $30.3797 \pm 0$      & $0.4924$   & $30.2785 \pm 0$\\
      SVM (RBF) + DBSCAN          & $0.9915$   & $25.9494 \pm 0$                & $1.4681$   & $22.7848 \pm 0$     & $1.4328$   & $\z{0.6329} \pm 0$   & $11.9417$  & $30.3797 \pm 0$          & $13.5147$  & $22.1519 \pm 0$      & $24.7346$  & $34.1772 \pm 0$\\
      SVM (sigmoid) + DBSCAN      & $3.5272$   & $28.4810 \pm 0$                & $6.4731$   & $20.2532 \pm 0$     & $1.5779$   & $30.3797 \pm 0$      & $0.9797$   & $36.0759 \pm 0$          & $0.5284$   & $22.1519 \pm 0$      & $0.8430$   & $24.6835 \pm 0$\\
      KNN-Brute-Force + kmeans    & $0.0236$   & $\bf{53.1646} \pm 0$           & $0.0343$   & $\bf{50.6329} \pm 0$& $0.0068$   & $\bf{43.0380} \pm 0$ & $0.0069$   & $\bf{43.0380} \pm 0$     & $0.0069$   & $36.0759 \pm 0$      & $0.0080$   & $41.7722 \pm 0$\\
      SVM (linear) + kmeans       & $1.7719$   & $25.3165 \pm 0$                & $37.9747$  & $37.9747 \pm 0$     & $0.2317$   & $25.3165 \pm 0$      & $0.8932$   & $27.8481 \pm 0$          & $0.2331$   & $24.0506 \pm 0$      & $0.1596$   & $20.2532 \pm 0$\\
      SVM (polynomial) + kmeans   & $1.0456$   & $25.3165 \pm 0$                & $1.4942$   & $26.5823 \pm 0$     & $0.2326$   & $14.5570 \pm 0$      & $0.4094$   & $28.4810 \pm 0$          & $0.2033$   & $24.0506 \pm 0$      & $0.4884$   & $25.3165 \pm 0$\\
      SVM (RBF) + kmeans          & $34.5382$  & $\z{8.8608} \pm 0$             & $43.0936$  & $29.7468 \pm 0$     & $110.589$  & $\z{0.6329} \pm 0$   & $112.945$  & $\z{1.2658} \pm 0$       & $38.7497$  & $22.7848 \pm 0$      & $14.1561$  & $27.2152 \pm 0$\\
      SVM (sigmoid) + kmeans      & $4.0277$   & $22.6582 \pm 0$                & $8.0918$   & $17.7848 \pm 0$     & $0.7529$   & $25.3165 \pm 0$      & $0.7967$   & $12.0253 \pm 0$          & $0.6921$   & $17.7215 \pm 0$      & $0.4013$   & $28.4810 \pm 0$\\
      Bayes-GA + kmeans           & $X$        & $X$                            & $X$        & $X$                 & $0.0294$   & $14.5570 \pm 0$      & $X$        & $X$                      & $0.0297$   & $15.8228 \pm 0$      & $X$        & $X$            \\
      \bottomrule
      \end{tabular}
    }
    \label{table:Arrhythmia_result}
      \vspace{-\baselineskip}
  \end{table*}

  \begin{table*}[tb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques. (gene expression cancer RNA-Seq dataset)}}
      \vspace{-\baselineskip}
    \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}lcccccccccccc@{}}\toprule
        Method                  & \multicolumn{2}{c}{Raw}        & \multicolumn{2}{c}{Normalized}     & \multicolumn{2}{c}{PCA-30}                & \multicolumn{2}{c}{PCA-30 Normalized} & \multicolumn{2}{c}{AE-30}         & \multicolumn{2}{c}{AE-30 Normalized} \\ 
        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
                                & Search (s) & acc               & Search (s) & acc                   & Search (s) & acc                          & Search (s) & acc                      & Search (s) & acc                  & Search (s) & acc            \\ \midrule
      KNN-Brute-Force + DBSCAN  & $14.5101$  & $59.0361 \pm 0$   & $10.3013$  & $\bf{66.5663} \pm 0$  & $0.0224$   & $94.5783 \pm 0$              & $0.0237$   & $78.3133 \pm 0$          & $0.0258$   & $\bf{64.4578} \pm 0$ & $0.0235$   & $59.3373 \pm 0$\\
      SVM (linear) + DBSCAN     & $124.593$  & $61.7470 \pm 0$   & $610.6730$ & $\z{9.9398} \pm 0$    & $0.6466$   & $\z{9.9398} \pm 0$           & $0.1193$   & $10.5422 \pm 0$          & $0.1407$   & $63.2530 \pm 0$      & $0.1122$   & $13.5542 \pm 0$\\
      SVM (polynomial) + DBSCAN & $81.6495$  & $61.7470 \pm 0$   & $86.6406$  & $\z{1.2048} \pm 0$    & $0.2585$   & $64.4578 \pm 0$              & $0.3012$   & $61.1446 \pm 0$          & $0.2013$   & $63.2530 \pm 0$      & $0.2056$   & $50.3012 \pm 0$\\
      SVM (RBF) + DBSCAN        & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $12.5077$  & $\z{9.9398} \pm 0$           & $3.8838$   & $63.2530 \pm 0$          & $5.0461$   & $40.3614 \pm 0$      & $11.4194$  & $49.6988 \pm 0$\\
      SVM (sigmoid) + DBSCAN    & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $0.6372$   & $71.6867 \pm 0$              & $0.8222$   & $65.9639 \pm 0$          & $0.6236$   & $44.2771 \pm 0$      & $0.2273$   & $38.2530 \pm 0$\\
      KNN-Brute-Force + kmeans  & $22.754$   & $\bf{74.0964} \pm 0$& $6.36577$& $53.6145 \pm 0$       & $0.0212$   & $\bf{94.8795} \pm 0$         & $0.0214$   & $\bf{84.9398} \pm 0$     & $0.0214$   & $42.1687 \pm 0$      & $0.0220$   & $\bf{65.9639} \pm 0$\\
      SVM (linear) + kmeans     & $136.408$  & $61.7470 \pm 0$   & $664.2860$ & $\z{9.9398} \pm 0$    & $0.5914$   & $\z{9.9398} \pm 0$           & $0.1077$   & $10.5422 \pm 0$          & $0.1274$   & $63.2530 \pm 0$      & $0.1084$   & $13.2530 \pm 0$\\
      SVM (polynomial) + kmeans & $81.4276$  & $61.7470 \pm 0$   & $81.1669$  & $63.8554 \pm 0$       & $0.2003$   & $64.4578 \pm 0$              & $0.2167$   & $25.3012 \pm 0$          & $0.1780$   & $63.2530 \pm 0$      & $0.1930$   & $50.3012 \pm 0$\\
      SVM (RBF) + kmeans        & $1772.32$  & $\z{9.9398} \pm 0$& $1800.6$   & $\z{9.9398} \pm 0$    & $1.3625$   & $\z{9.9398} \pm 0$           & $1.3848$   & $\z{9.9398} \pm 0$       & $11.1729$  & $39.7590 \pm 0$      & $4.7882$   & $28.6145 \pm 0$\\
      SVM (sigmoid) + kmeans    & $190.866$  & $26.5060 \pm 0$   & $81.7487$  & $63.8554 \pm 0$       & $0.8287$   & $65.9639 \pm 0$              & $0.4269$   & $65.9639 \pm 0$          & $0.9908$   & $28.9157 \pm 0$      & $0.2360$   & $39.4578 \pm 0$\\
      Bayes-GA + kmeans         & $X$        & $X$               & $X$        & $X$                   & $X$        & $X$                          & $X$        & $X$                      & $0.0338$   & $27.7946 \pm 0$      & $X$        & $X$            \\
      \bottomrule
      \end{tabular}
    }
    \label{table:gene_expression_result}
      \vspace{-\baselineskip}
  \end{table*}

@@

\section{Contribution}
\begin{itemize}
  \item Hsieh Cheng-Han: KNN, SVM, DBSCAN, paper, ppt
  \item Hsu Ting-Hao: 
  \item Sun Shih-Yu: SVM, k-means, paper
  \item Lu Che-Yuan: 
  \item Huang Chia-Yen: naive Bayes classifier, paper, poster
\end{itemize}

>>>>

  \begin{table*}[tb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques. (Arrhythmia dataset)}}
      \vspace{-\baselineskip}
    \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}lcccccccccccc@{}}\toprule
        Method                    & \multicolumn{2}{c}{Raw}                     & \multicolumn{2}{c}{Normalized}   & \multicolumn{2}{c}{PCA-32}        & \multicolumn{2}{c}{PCA-32 Normalized} & \multicolumn{2}{c}{AE-32}        & \multicolumn{2}{c}{AE-32 Normalized} \\ 
        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
                                  & Search (s) & acc                            & Search (s) & acc                 & Search (s) & acc                  & Search (s) & acc                      & Search (s) & acc                  & Search (s) & acc            \\ \midrule
      KNN-Brute-Force + DBSCAN    & $0.0285$   & $47.4684 \pm 0$                & $0.0254$   & $46.8354 \pm 0$     & $0.0070$   & $38.6076 \pm 0$      & $0.0071$   & $42.4051\pm 0$           & $0.0071$   & $\bf{37.9747} \pm 0$ & $0.0071$   & $\bf{44.3038} \pm 0$\\
      SVM (linear) + DBSCAN       & $1.7269$   & $25.9494 \pm 0$                & $8.9285$   & $35.4430 \pm 0$     & $0.2186$   & $32.2785 \pm 0$      & $0.8162$   & $29.7468 \pm 0$          & $0.2169$   & $31.6456 \pm 0$      & $0.1552$   & $27.8481 \pm 0$\\
      SVM (polynomial) + DBSCAN   & $0.9993$   & $25.9494 \pm 0$                & $1.6100$   & $25.3165 \pm 0$     & $0.1997$   & $\z{1.2658} \pm 0$   & $0.4577$   & $33.5443 \pm 0$          & $0.2402$   & $30.3797 \pm 0$      & $0.4924$   & $30.2785 \pm 0$\\
      SVM (RBF) + DBSCAN          & $0.9915$   & $25.9494 \pm 0$                & $1.4681$   & $22.7848 \pm 0$     & $1.4328$   & $\z{0.6329} \pm 0$   & $11.9417$  & $30.3797 \pm 0$          & $13.5147$  & $22.1519 \pm 0$      & $24.7346$  & $34.1772 \pm 0$\\
      SVM (sigmoid) + DBSCAN      & $3.5272$   & $28.4810 \pm 0$                & $6.4731$   & $20.2532 \pm 0$     & $1.5779$   & $30.3797 \pm 0$      & $0.9797$   & $36.0759 \pm 0$          & $0.5284$   & $22.1519 \pm 0$      & $0.8430$   & $24.6835 \pm 0$\\
      KNN-Brute-Force + kmeans    & $0.0236$   & $\bf{53.1646} \pm 0$           & $0.0343$   & $\bf{50.6329} \pm 0$& $0.0068$   & $\bf{43.0380} \pm 0$ & $0.0069$   & $\bf{43.0380} \pm 0$     & $0.0069$   & $36.0759 \pm 0$      & $0.0080$   & $41.7722 \pm 0$\\
      SVM (linear) + kmeans       & $1.7719$   & $25.3165 \pm 0$                & $37.9747$  & $37.9747 \pm 0$     & $0.2317$   & $25.3165 \pm 0$      & $0.8932$   & $27.8481 \pm 0$          & $0.2331$   & $24.0506 \pm 0$      & $0.1596$   & $20.2532 \pm 0$\\
      SVM (polynomial) + kmeans   & $1.0456$   & $25.3165 \pm 0$                & $1.4942$   & $26.5823 \pm 0$     & $0.2326$   & $14.5570 \pm 0$      & $0.4094$   & $28.4810 \pm 0$          & $0.2033$   & $24.0506 \pm 0$      & $0.4884$   & $25.3165 \pm 0$\\
      SVM (RBF) + kmeans          & $34.5382$  & $\z{8.8608} \pm 0$             & $43.0936$  & $29.7468 \pm 0$     & $110.589$  & $\z{0.6329} \pm 0$   & $112.945$  & $\z{1.2658} \pm 0$       & $38.7497$  & $22.7848 \pm 0$      & $14.1561$  & $27.2152 \pm 0$\\
      SVM (sigmoid) + kmeans      & $4.0277$   & $22.6582 \pm 0$                & $8.0918$   & $17.7848 \pm 0$     & $0.7529$   & $25.3165 \pm 0$      & $0.7967$   & $12.0253 \pm 0$          & $0.6921$   & $17.7215 \pm 0$      & $0.4013$   & $28.4810 \pm 0$\\
      Bayes-GA + kmeans           & $0.1342$   & $13.2911 \pm 0$                & $X$        & $X$                 & $0.0294$   & $14.5570 \pm 0$      & $0.0400$   & $31.6456 \pm 0$          & $0.0297$   & $15.8228 \pm 0$      & $0.0399$   & $31.6456 \pm 0$\\
      \bottomrule
      \end{tabular}
    }
    \label{table:Arrhythmia_result}
      \vspace{-\baselineskip}
  \end{table*}

  \begin{table*}[tb]
    \newcommand{\z}{\phantom{0}}
    \caption{\textsc{Comparison of Classification Techniques. (gene expression cancer RNA-Seq dataset)}}
      \vspace{-\baselineskip}
    \resizebox{\textwidth}{!}{
      \begin{tabular}{@{}lcccccccccccc@{}}\toprule
        Method                  & \multicolumn{2}{c}{Raw}        & \multicolumn{2}{c}{Normalized}     & \multicolumn{2}{c}{PCA-30}                & \multicolumn{2}{c}{PCA-30 Normalized} & \multicolumn{2}{c}{AE-30}         & \multicolumn{2}{c}{AE-30 Normalized} \\ 
        \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}
                                & Search (s) & acc               & Search (s) & acc                   & Search (s) & acc                          & Search (s) & acc                      & Search (s) & acc                  & Search (s) & acc            \\ \midrule
      KNN-Brute-Force + DBSCAN  & $14.5101$  & $59.0361 \pm 0$   & $10.3013$  & $\bf{66.5663} \pm 0$  & $0.0224$   & $94.5783 \pm 0$              & $0.0237$   & $78.3133 \pm 0$          & $0.0258$   & $\bf{64.4578} \pm 0$ & $0.0235$   & $59.3373 \pm 0$\\
      SVM (linear) + DBSCAN     & $124.593$  & $61.7470 \pm 0$   & $610.6730$ & $\z{9.9398} \pm 0$    & $0.6466$   & $\z{9.9398} \pm 0$           & $0.1193$   & $10.5422 \pm 0$          & $0.1407$   & $63.2530 \pm 0$      & $0.1122$   & $13.5542 \pm 0$\\
      SVM (polynomial) + DBSCAN & $81.6495$  & $61.7470 \pm 0$   & $86.6406$  & $\z{1.2048} \pm 0$    & $0.2585$   & $64.4578 \pm 0$              & $0.3012$   & $61.1446 \pm 0$          & $0.2013$   & $63.2530 \pm 0$      & $0.2056$   & $50.3012 \pm 0$\\
      SVM (RBF) + DBSCAN        & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $12.5077$  & $\z{9.9398} \pm 0$           & $3.8838$   & $63.2530 \pm 0$          & $5.0461$   & $40.3614 \pm 0$      & $11.4194$  & $49.6988 \pm 0$\\
      SVM (sigmoid) + DBSCAN    & $X$        & $\text{not converge}$ & $X$    & $\text{not converge}$ & $0.6372$   & $71.6867 \pm 0$              & $0.8222$   & $65.9639 \pm 0$          & $0.6236$   & $44.2771 \pm 0$      & $0.2273$   & $38.2530 \pm 0$\\
      KNN-Brute-Force + kmeans  & $22.754$   & $\bf{74.0964} \pm 0$& $6.36577$& $53.6145 \pm 0$       & $0.0212$   & $\bf{94.8795} \pm 0$         & $0.0214$   & $\bf{84.9398} \pm 0$     & $0.0214$   & $42.1687 \pm 0$      & $0.0220$   & $\bf{65.9639} \pm 0$\\
      SVM (linear) + kmeans     & $136.408$  & $61.7470 \pm 0$   & $664.2860$ & $\z{9.9398} \pm 0$    & $0.5914$   & $\z{9.9398} \pm 0$           & $0.1077$   & $10.5422 \pm 0$          & $0.1274$   & $63.2530 \pm 0$      & $0.1084$   & $13.2530 \pm 0$\\
      SVM (polynomial) + kmeans & $81.4276$  & $61.7470 \pm 0$   & $81.1669$  & $63.8554 \pm 0$       & $0.2003$   & $64.4578 \pm 0$              & $0.2167$   & $25.3012 \pm 0$          & $0.1780$   & $63.2530 \pm 0$      & $0.1930$   & $50.3012 \pm 0$\\
      SVM (RBF) + kmeans        & $1772.32$  & $\z{9.9398} \pm 0$& $1800.6$   & $\z{9.9398} \pm 0$    & $1.3625$   & $\z{9.9398} \pm 0$           & $1.3848$   & $\z{9.9398} \pm 0$       & $11.1729$  & $39.7590 \pm 0$      & $4.7882$   & $28.6145 \pm 0$\\
      SVM (sigmoid) + kmeans    & $190.866$  & $26.5060 \pm 0$   & $81.7487$  & $63.8554 \pm 0$       & $0.8287$   & $65.9639 \pm 0$              & $0.4269$   & $65.9639 \pm 0$          & $0.9908$   & $28.9157 \pm 0$      & $0.2360$   & $39.4578 \pm 0$\\
      Bayes-GA + kmeans         & $2.231$    & $43.6746$         & $X$        & $X$                   & $0.0327$   & $34.0361 \pm 0$              & $0.0364$   & $16.8675 \pm 0$          & $0.0338$   & $27.7946 \pm 0$      & $0.0427$   & $16.8674 \pm 0$\\
      \bottomrule
      \end{tabular}
    }
    \label{table:gene_expression_result}
      \vspace{-\baselineskip}
  \end{table*}

@@

\section{Contribution}
\begin{itemize}
  \item Hsieh Cheng-Han: KNN, SVM, DBSCAN, paper, ppt
  \item Hsu Ting-Hao: 
  \item Sun Shih-Yu: SVM, k-means, paper
  \item Lu Che-Yuan: naive Bayes classifier
  \item Huang Chia-Yen: naive Bayes classifier, paper, poster
\end{itemize}
